Printer ballistics through texture analysis of characters

### 2013-11-28 Printer_Ballistics.tex
After lunch

\begin{table*}
\caption{Printers used in this work}
\label{tab:printers}
\begin{center}
    \begin{tabular}{ | c | c | c | c |}
    \hline
Printer & Documents & Characters ''e'' & Characters ''t'' \\ \hline
Brother-HL4070CDW & 28 & 252 & 252\\
Canon-D1150 & 28 & 252 & 252\\
Canon-MF3240 & 28 & 252 & 252\\
Canon-MF4370DN & 27 & 252 & 252 \\
HP-CLJ-CP2025A & 28 & 250 & 250\\
HP-JL-CP1518 & 0 & 0 & 0\\
Lexmark-E260D & 0 & 0 & 0\\
OKI-C330 & 0 & 0 & 0\\
Samsung-CLP315 & 0 & 0 & 0 \\
\hline
    \end{tabular}
\end{center}    
\end{table*}

@@

@@

\section{Formulas}
\subsection{Contrast}

@@

>>>>

\begin{table*}
\caption{Printers used in this work}
\label{tab:printers}
\begin{center}
    \begin{tabular}{ | c | c | c | c |}
    \hline
Printer & Documents & Characters ''e'' & Characters ''t'' \\ \hline
Brother-HL4070CDW & 28 & 252 & 252\\
Canon-D1150 & 28 & 252 & 252\\
Canon-MF3240 & 28 & 252 & 252\\
Canon-MF4370DN & 27 & 252 & 252 \\
HP-CLJ-CP2025A & 28 & 250 & 250\\
Lexmark-E260D & 30 & 636 & 629\\
\hline
    \end{tabular}
\end{center}    
\end{table*}

@@

\newpage

@@

\section{Formulas}

$p$ represents the pixel-of-interest.

$i$ and $j$ represents the positions of the values of the co-occurrence matrix.

$\mu i$ and $\mu j$ represents the mean of $i$ and $j$, respectively.

$\sigma i$ and $\sigma j$ represents the standard deviation of $i$ and $j$, respectively.

\subsection{Contrast}

@@

\subsection{Homogeneity}

Returns a value that represents the relative proximity of the diagonal elements of the co-occurrence matrix. The range of possible values is between 0 and 1, and the value 1 represents a diagonal matrix.

$$\sum_{i,j} \frac{p(i, j)}{1 + \vert i - j \lvert}$$
